|

### 2021-06-13 01-Chp-Background.Rmd
End of day: -3162

$$TC \approx LDLc - HDLc - kTG$$
where $k$ is 0.20 if measurements are in milligrams per decilitre (_mg/dl_) and 0.45 if measured in millimole per litre (_mmol/l_).

>>>>

$$TC \approx LDLc + HDLc + kTG$$
where $k$ is 0.20 if measurements are in milligrams per decilitre (_mg/dl_) and 0.45 if measured in millimole per litre (_mmol/l_).

### 2021-06-13 03-Chp-Systematic-Review.Rmd
End of day: -3162

The following databases will be searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection (for the specific databases available thi via the Univeristy ). We will also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials. As the contents of the Web of Science Core COllection can vary by institution, the specific database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).

The abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) will be searched. <!-- TODO how were these searched? -->
 Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal. We will also search bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies. Finally, the reference lists of included studies will be searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).

@@

### Following up with authors

@@

#### Simple meta-analysis

@@

Need formula here, and description of different methods and quarrels re fixed effect vs random effects meta-analyses.

This anal

Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on.

@@

<!-- TODO Explore how to map from simple diagnosis of hyperchol to dose response. Seems that does response needs > 3 categories -->

Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g. for example, highest vs lowest quartile). while this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.

Where possible, data for all exposure groups was extracted, and this. Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not presented (e.g. if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands in mmol/L)

Note that

@@

@@

@@

<!-- TODO This needs to use the PRISMA2020 package -->

@@

(ref:prisma-flow-cap) **PRISMA Flowchart:** Overview of how records moved through the systematic review process

(ref:prisma-flow-scap) PRISMA Flow Diagram

@@

@@

-   Summary of locations

@@

Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] __[ALSO CITE WILKINSON AND MCGUINNESS HERE]__.

>>>>

The following databases will be searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection (for the specific databases available thi via the University). We will also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials. As the contents of the Web of Science Core COllection can vary by institution, the specific database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).

The abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) will be searched. <!-- TODO how were these searched? -->

 Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal. We will also search bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies. Finally, the reference lists of included studies will be searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).

@@

### Following up with authors {#contacting-authors}

@@

#### Standard meta-analysis

@@

Need formula here, and description of different methods and quarrels regarding disctinction fixed effect vs random effects meta-analyses.

This analytical approach was used for

@@

<!-- TODO Explore how to map from simple diagnosis of hyperchol to dose response. Seems that does response needs >3 categories -->
<!-- Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on.  -->

Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g. for example, highest vs lowest quartile). <!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results? -->
 while this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.

Where possible, data for all exposure groups was extracted, and this. Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not presented (e.g. if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands in mmol/L).

<!-- TODO Do I initially want to fit a linear relationship across categories and  -->
A XXXX spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of an exposure can have an effect versus the "normal" reference dose. Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fractions, as detailed in Table \@ref(tab:lipidLevels-table). Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.

Due to the requirements for the dose response analysis, studies were excluded from this secondary analysis if they did not provide the require information: cut-off points. Where this was not reported in the study, I contacted the corresponding author to attempt to obtain the required information (see \@ref(contacting-authors)).

@@

I conducted a leave one out analysis in order to explore the impact of any given study on the results. <!-- TODO CITATION NEEDED -->

In addition,

@@

### Deviations from the protocol

A dose response meta-analysis was not planned, marking a departure from the register protocol. <!-- TODO Check this is accurate -->

@@

@@

(ref:prisma-flow-cap) PRISMA Flow diagram illustrating how records moved through the systematic review process. The different contributions of databases and preprint servers to the review are indicated.

(ref:prisma-flow-scap) PRISMA flow diagram

@@

A PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram,[@page2021] shown in Figure \@ref(prisma-flow-fig), shows the movement of articles through the review. To illustrate the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the right of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the left of the diagram).

Of note, preprints and published papers reporting the same study were not considered duplicate records. Instead, they were considered as different reports of the same study. This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.

@@

-   Summary of locations (use evidence map)

@@

Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019d; @wilkinson2018b]

### 2021-06-13 05-Chp-IPD-Analysis.Rmd
End of day: -3464
End of day: -3162

@@

@@

@@

This is likely due to my junior position as a early a

Range of reasons why data is not readily available.

@@

Describe your experience of trying to access the DPUK - while a great resources, furstrating at times.

>>>>

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
Hold
```
(ref:intro-quote) --- Hold

@@

Is there a good way to visualise input of cohorts into an IPD analysis?

@@

Talk about how different covariates were managed across cohorts,

Talk about missing data was handled <!-- IDEA See Sean's thesis for some additional detail on this -->

@@

This is likely due to my junior position as a early career research combined with the impact

Range of reasons why data is not readily available. Privacy concerns, concerns around scoping or "parasitic" behaviour, and a lack of trust (i.e. primary researchers do not trust secondary researchers).<!-- TODO CITATION NEEDED: paper on trust as a big issue + paper on systematic review of barriers to data sharing -->

@@

### Reflections on data access

Describe your experience of trying to access the DPUK - while a great resources, frustrating at times. The portal would benefit from a centralised management system and
